Karpov, Kasparov, Anand

### 2022-05-31 inst/kka.Rmd
update text

---
title: "Karpov, Kasprov, Anand"
output: html_document
---

@@

@@

This file defines dataset `kka` which is the observed scorelines
between the three players.  It is used to calculate likelihood
functions: `karpov_kasparov_anand`, `kka_3whites` and `kka_3draws`
This Rmd file supercedes files `inst/karpov_kasparov_anand.R` and
`inst/kka_3draws.R` and `inst/kka_array.R`.  Some more detail is given
in `man/karpov_kasparov_anand.Rd`.

@@

for the observation of $+a\,=0\,-b$ for $p_1$ playing white and
$+c\,=0\,-d$ for $p_2$ playing white.  We then translate this into a
`hyper3` likelihood function as follows

@@

Above we see a credible interval for $\lambda$ being about
$(1.4,2.9)$.  Of course, this is crude and it would be betterto have
more transparent package idiom.  But I'm working on this.

@@

```{r,createchess3}
jj <- round(o$par,2)
(chess3 <-  white_draw3(kka_array, lambda=jj[1],D=jj[2]))
(chess3_maxp <-  maxp(chess3))
```

>>>>

---
title: "Karpov, Kasparov, Anand"
output: html_document
---

@@

(takes about 45 minutes to process without cache)

@@

This file defines dataset `kka` which is the observed scorelines
between players Karpov, Kasparov, and Anand.  It is used to calculate
likelihood functions: `karpov_kasparov_anand`, `kka_3whites` and
`kka_3draws`.  This Rmd file supercedes files
`inst/karpov_kasparov_anand.R` and `inst/kka_3draws.R` and
`inst/kka_array.R`.  Some more detail is given in
`man/kka.Rd`.

@@

for the observation of $+a$ $\text{=}0$ $-b$ for $p_1$ playing white
and $+c$ $\text{=}0$ $-d$ for $p_2$ playing white.  We then translate
this into a `hyper3` likelihood function as follows

@@

Above we see a credible interval for $\lambda$ being about
$(1.4,2.9)$.  Of course, this is crude and it would be better to have
more transparent package idiom.  But I'm working on this.

@@

```{r,createchess3,cache=TRUE}
jj <- round(o$par,2)
(chess3 <-  white_draw3(kka_array, lambda=jj[1],D=jj[2]))
(chess3_maxp <-  maxp(chess3))
```
